Risk Perceptions for Wearable Devices

### 2015-02-20 paper.tex
cleanup

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{acm_proc_article-sp}

\usepackage{color}

%%% still need to break urls

\usepackage[hyphens]{url}

\def\etal{{\it et al.~}}

\newenvironment{packed_enum}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}}

\newenvironment{packed_item}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

@@

\title{Risk Perceptions for Wearable Devices}
%\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}

%\subtitle{[Extended Abstract]
%\titlenote{Note
%\textit{Note \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.website.com}}}

%\numberofauthors{1}
%\author{
% \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
%   \vspace{0.5em}
%   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
%   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
%}

\numberofauthors{1}
\author{
 \alignauthor Anonymous\\
   \vspace{0.5em}
   \affaddr{Some Place}
}

\maketitle
\begin{abstract}
We performed an online survey to examine risk perceptions surrounding wearable computing devices. We examine different data types that might be captured,  and the effect of who the data is shared with. We surveyed 1,784 participants about 88 data types and 4 data recipients to quantify risk perceptions across a wide range of scenarios, and evaluate of which factors contribute to the severity of these risks. Following previous work, we also asked participants to perform a risk/benefit analysis of 20 new technologies along with other well-understood technologies. The results of this study can be used to guide future research in wearable device security, especially research that helps protect sensitive data and design effective privacy notifications or indicators.
\end{abstract}

% A category with the (minimum) three required fields
\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]

%\terms{Human Factors}{Measurement}{Security}

\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings

%%%%%%%%%%%%%%%%%%%
%%%         PAPER BODY         %%%
%%%%%%%%%%%%%%%%%%%

\section{Introduction}
With their ability to constantly capture data and help users, wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing. Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking. Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and a top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.

The market for wearable devices is currently in infancy. It is hard to predict what device and applications will be most popular, but we use the current interest as a baseline. A survey of 3,956 respondents with high interest in wearables found that, currently, the most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}. It is estimated that 20\% of the general population owns at least one wearable and 10\% use at least one in their daily lives~\cite{WearableStatNews}. Most wearables consumers are young (48\% are between 18 and 34), but this \$700 million industry will reach other demographics soon~\cite{cmo}.

Wearable devices bring with them new potential security and privacy concerns. Many concerns exposure of users' activities without their awareness or consent. For instance, Fitbit's fitness profiles were public by default and also allowed sex to be tracked as exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information. Additionally, public discomfort prevented companies from enabling capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.

To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}. A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns. The goal of this paper is to gain a better sense of what those concerns are.

We surveyed 1,784 Internet users for their perceptions of wearable devices. In this work, we contribute the following: \\[-0.8cm]

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item We compare users' perceptions of a range of privacy and security risks of wearables. Users care much more about the type of data, than the recipient of the data.
\item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
\item Our participants viewed data-collection capabilities of wearable devices as benign compared to more familiar technologies. However, we suspect that this may be due to a lack of exposure to these newer technologies.
%\item We report people's self-reported top concerns for wearable devices. Privacy, by far, is the top concern. Other notable risks include information security, long-term health risks from use, high financial cost, and change in social norms. 
\end{itemize}

%%%%%%%%%%%%%%%%%%%

\section{Methodology}

Our survey contained two main sections.
In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
This was intended to elicit their perception of the severity and impact of the risk.
In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception by Fischhoff \etal \cite{Fischhoff}.
Our survey design is based on two prior perception studies, as we describe next.

%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.

%LL: this commented out for anonymity; can comment back in later.
%%% The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.

%::LL: David, I spliced the related work; the text related to work directly related to our research to introduce/motivate the methodology remains here. The rest were put at the end of the paper, as you requested.

\subsection{Methodology Motivation}
\subsubsection{Smartphone Risk Scenarios}
Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risk scenarios. Participants were asked how upset they would be if a certain action had occurred without permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
Our methodology closely follows that study, but with different scenarios chosen to shed light on security and privacy risks of wearable devices.

\subsubsection{Technology Risk Perception}
Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}. In their study, participants were asked to separately rate the risks and benefits for those technologies. They were told to think about all people affected by the technology, and to think about long-term vs. short-term risks and benefits. Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.

%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.

\subsection{Survey Questions}
In our survey, each participant answered 27 questions, across five different sections:   \\[-.8cm]

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item 2 comprehension questions
\item 6 questions about wearable computing scenarios 
\item 2 questions about smartphone scenarios 
\item 2 risk/benefit questions 
\item 15 demographic questions \\[-.8cm]
\end{itemize}

We randomized the order participants saw sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.

\subsubsection{Comprehension Questions}
Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable. Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks. We highlighted the capabilities of this device and described use cases. To ensure that participants had read and understood this device's capabilities, we ask them two multiple-choice comprehension questions.

\subsubsection{Wearables Scenarios}
We presented scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking first (see Figure \ref{fig:prompt}). Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}. Our questions were of the format:

\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.

We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]

\begin{figure}[t]
	\centering
	\includegraphics[width=0.47\textwidth]{prompt.pdf}
	\caption{An example of a wearable scenario question participants saw while taking the survey.}
	\label{fig:prompt}
\end{figure}

\begin{packed_item}
\item Your work contacts
\item Your friends
\item The public
\item The app's server (but didn't share it with anyone else)\\[-.8cm]
\end{packed_item}

The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared. Additionally, we added 16 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we found relevant nonetheless. An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' There were a total of 304 questions in this set, from which we randomly 6 questions for each participant.

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}
We presented participants with a second set of scenarios to control for the type of device being used. These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}. We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]

\begin{packed_enum}
\item \textit{How would you feel if an app on your smartphone vibrated your phone without asking you first?}
\item \textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}
\item \textit{How would you feel if an app on your smartphone un-muted a phone call without asking you first?}
\item \textit{How would you feel if an app on your smartphone took screenshots when you were using other apps, without asking you first?}
\item \textit{How would you feel if an app on your smartphone sent premium (they cost money) calls or text messages, without asking you first?} 
\end{packed_enum}

\subsubsection{Risk and Benefit Assessment}
In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies. We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society. We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity, which were chosen to span varying levels of risks and benefits.

Alongside the 4 studied technologies, we asked participants to evaluate one of 20 technologies relevant to wearables: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection. We asked about familiar technologies such as the internet, general and specific wearable artifacts, and a range of new capabilities.

%LL: we didn't pick it because they were studied by this study, so this is a bit distracting, especially since the related work is at the end instead of before this.. 
%Many of these technologies were selected from those studied by Egelman \etal\cite{Egelman2015}.

To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved. We randomized whether they performed the ranking for risks or benefits first. The prompt is listed in Appendix \ref{sec:prompt}. The question format was as follows:

\textit{Fill in your <risk/benefit> numbers for the following:}\\[-.5cm]

\textit{Handguns}: \_\_\_\_\_\_\_ \\
\textit{Motorcycles}: \_\_\_\_\_\_\_\\
\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
\textit{<Wearable Technology>}: \_\_\_\_\_\_\_\\
\textit{Electricity}: \_\_\_\_\_\_\_\\ [-.5cm]

\subsubsection{Additional Questions}
The exit portion of the survey firstly consisted of questions asking for age, gender, and education. Then, we asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices. We end with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.

\subsection{Focus Group}
We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue. The focus group began with participants taking the survey. Afterward, we asked participants to give feedback on the format and the content, noting any instructions or questions that were unclear. The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional scenarios to include. Finally, we compensated participants with \$30 in cash. We recruited all of our focus group participants from Craigslist. Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).  Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.

\subsection{Recruitment and Analysis Method}
We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk. We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above. Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants. We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784. Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).

In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.  The VUR is defined as the percentage of participants who reported a `5' on the Likert scales. 
We use the VURs rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced. Additionally, most were be upset, at least a little, in all scenarios when a device takes action without permission (rating distribution: ``1''= 455, ``2'' = 523, ``3'' = 902, ``4''' = 1,746, ``5'' = 6,654). Thus, the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.

In this section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses. Rather, we report medians and quartiles, which are not impacted by outliers. For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%. The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.

%%%%%%%%%%%%%%%%%%%

\section{Results}
In this section, we present our survey results. We first discuss participants' responses to the various data-sharing scenarios, and how data type, data recipient, and device contributed to how threatening a situation was perceived. Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies. We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.

\subsection{Concern Factors}
In this section, we discuss factors impacting participants' concern levels for each scenario: the data recipient, the data type, and whether or not the scenario occurred on a wearable or a smartphone. We analyze each factor individually, as well as present a statistical model of participants' concerns as a function of all of factors, including demographic traits.

\subsubsection{Data Type}
Based on our data, we observed that the largest effect stemmed from the data type being shared in a scenario. We present various statistical models in section \ref{sec:regression} to support this conclusion. Due to space limitations, we are unable to show results of the statistical analyses respect to the significance of the VUR rankings of the 88 data types. The 10 most and 10 least concerning data types can be seen in Table \ref{top10}.

Regardless of the data recipient or the device, participants were most concerned about photos and videos, especially if they contained embarrassing content, nudity, or financial information. As seen in Table \ref{top10}, photos and videos accounted for 5 of the top 10 concerns. Information that could be used to impersonate someone (e.g., usernames/passwords for websites) or invade privacy (photos of someone at home) were also among the most concerning data types.

Also regardless of the data recipient, the least concerning data types mostly consisted of information that could be observed through observations of public behavior, such as demographic information (e.g., age, gender, language spoken). It is possible that people rated these as unconcerning because they think many entities already track this data (e.g., shows watched, music listened to, exercise patterns).

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| r | l | r |}
\hline
Rank & Data &  VUR  \\
\hline
1 & a video of you unclothed & 95.97\% \\
2 & bank account information & 95.91\% \\
3 & social security number & 94.84\% \\
4 & video of you entering in your PIN & 92.67\% \\
5 & a photo of you unclothed & 92.59\% \\
6 & an incriminating/embarrassing photo of you & 91.39\% \\
7 & username and password for websites & 89.55\% \\
8 & credit card information & 88.98\% \\
9 & an incriminating/embarrassing video of you & 88.41\% \\
10 & a random (inward-facing) photo you at home & 87.50\% \\
 & \vdots & \\
64 & eye movement patterns (for eye tracking) & 40.51\% \\
65 & when and how much you exercise  & 38.66\% \\
66 & when you are happy or having fun  & 34.75\% \\
67 & which television shows you watch & 30.20\% \\
68 & when you are busy or interruptible  & 29.50\% \\
69 & music from your device  & 28.06\% \\
70 & your heart rate & 27.50\% \\
71 & your age & 24.29\% \\
72 & the language you speak & 15.86\% \\
73 & your gender & 15.00\% \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

%A statistical analysis regarding the significance and confidence of <data> types with respect to all 72 was not performed due to the space constraints of the paper. We do consider all <data> categories in our statistical model, which provides an analysis of what factors had contributed to the perceived severity of a particular situation.

\subsubsection{Data Recipient}
Across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher. A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}). However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).

We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios. But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results. Nonetheless, we repeated the analysis using only one randomly-selected data point per participant to find that the test was robust to this violation. Participants were significantly more concerned about having their data seen by humans ({\it vis-{\`a}-vis} app servers), though differences between specific human groups (between the public, friends, and work contacts) were not significant.

%Comment on differences between public/work, and end the subsection
%SE: this needs to be rewritten below.

We compared the 10 most concerning scenarios when sharing with an app servers versus with a humans. We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]

\begin{packed_enum}
\item Bank account information
\item A video of you unclothed
\item Social security number
\item Video of you entering your PIN
\item An incriminating/embarrassing photo of you
\item A photo of you unclothed \\[-.8cm]
\end{packed_enum}

While the concerning data types do not appreciably change based on the data recipient---even the non-overlapping scenarios all dealt with confidential data (e.g., passcode, credit card information, etc.)---only the level of concern changed. For instance, the 10th most concerning scenario for the non-human audience had a VUR of 66.67\%, whereas the 10th most concerning scenario for a human audience has a VUR of 93.88\%. This suggests that concern for different data types does not appear to vary relative to other data types based on recipient, but instead the recipient determines the overall magnitude of the concern.\\

%\begin{table}[t]
%\begin{center}
%\begin{tabular}{|l|r|}
%\hline
%Recipients & VUR \\
%\hline
%App &  42.3\% \\
%Friends & 69.5\% \\
%Work & 75.2\% \\
%Public & 72.4\% \\ 
%\hline
%\end{tabular}
%\caption{generated for my presentation.}
%\label{nouse}
%\end{center}
%\end{table}

\begin{table}[t]
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
\hline
Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
\hline
Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
\hline
\end{tabular}
\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
\label{recipient}
\end{center}
\end{table}

%\begin{table}[t]
%\begin{center}
%\begin{tabular}{|l|r|r|r|r|}
%\hline
%Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
%\hline
%Work-App	& 42.49	& <0.0001	&	601	&	0.071\\
%Public-App &	48.52	& <0.0001	&		636	&	0.076\\
%Friends-App	& 32.07	& <0.0001	&		609	&	0.053\\
%Friends-Work & 	0.87 &	<0.3517	&	604	&	0.001\\
%Friends-Public	& 1.46 &	<0.2229	&	639	&	0.002\\
%Work-Public &	0.67 &	<0.7956	&		631	&	0.001\\
%\hline
%\end{tabular}
%\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
%\label{recipient}
%\end{center}
%\end{table}

%\begin{table}[t]
%\begin{center}
%\begin{tabular}{| c | c | c | c |}
%Recipients	& $\chi^2$ &	2-tail P &  Effect Size \\
%Work-App	& 564.318 & <0.0001 & 0.111\\
%Public-App	& 479.980 & <0.0001 &  0.092\\
%Friends-App & 380.000 & <0.0001 & 0.075\\
%Friends-Work & 20.365 & <0.0001 &  0.004\\
%Friends-Public & 5.349 & 0.0207 &  0.001\\
%Work-Public&  5.054 & 0.0246 &  0.001\\
%\end{tabular}
%\caption{Chi-Squared test results of the effects of various recipients contributing to VUR.}
%\label{recipient}
%\end{center}
%\end{table}

%\begin{table}[t]
%\begin{center}
%\begin{tabular}{| l | c |}
%<data> & VUR  \\
%social security number & 98.04\% \\ CC
%a video of you unclothed & 97.44\% \\ CC
%bank account information & 97.10\% \\ CC
%recordings of your work conversations & 96.97\% \\ 
%an incriminating/embarrassing photo of you & 96.36\% \\ CC
%a photo of you unclothed & 96.30\% \\ CC
%credit card information & 95.92\% \\ 
%username and password for websites & 95.41\% \\ 
%a video of you entering in your PIN & 93.91\% \\ CC
%recordings of your phone conversations & 93.88\% \\ 
%\end{tabular}
%\caption{A table of the top 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
%\label{sharedtop10}
%\end{center}
%\end{table}
%
%\begin{table}[t]
%\begin{center}
%\begin{tabular}{| l | c |}
%%starting from #63
%<data> &  VUR  \\
%bank account information & 90.91\% \\ CC
%a video of you unclothed & 90.62\% \\ CC
%social security number  & 88.68\% \\ CC
%video of you entering your PIN & 88.57\% \\ CC
%an incriminating/embarrassing photo of you & 78.05\% \\ CC
%a photo of you unclothed & 77.78\% \\ CC
%a video of you entering a passcode to a door & 75.00\% \\ 
%when and how much you have sex & 73.08\% \\ 
%an incriminating/embarrassing video of you & 71.88\% \\ 
%a random (inward-facing) photo of you at home & 66.67\% \\
%\end{tabular}
%\caption{A table of the top 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
%\label{notsharedtop10}
%\end{center}
%\end{table}
%
%\begin{table}[t]
%\begin{center}
%\begin{tabular}{| l | c |}
%%starting from #63
%<data> &  VUR  \\
%your name & 47.25\% \\
%when and how much you exercise & 46.07\% \\
%when you were happy or having fun & 38.10\% \\
%what television shows you watch & 35.96\% \\
%when you are busy or interruptible & 34.34\% \\
%your heart rate & 32.28\% \\
%music from your device & 31.87\% \\
%your age & 29.67\% \\
%the language you speak & 20.95\% \\
%your gender & 16.81\% \\
%\end{tabular}
%\caption{A table of the bottom 10 upsetting <data> types, with respect to <recipient> types friends, work, and public.}
%\label{sharedbottom10}
%\end{center}
%\end{table}
%
%
%\begin{table}[t]
%\begin{center}
%\begin{tabular}{| l | c |}
%%starting from #63
%<data> &  VUR  \\
%when and how much you exercise & 16.67\% \\
%how much you use your phone & 15.79\% \\
%your age & 14.29\% \\
%how much you like the people you interact with & 13.79\% \\
%when, what, and how much you ate & 12.50\% \\
%which television shows you watch & 11.43\% \\
%your gender & 9.52\% \\
%your heart rate & 9.09\% \\
%eye movement patterns (for eye tracking) & 6.98\% \\
%the language you speak & 2.50\% \\
%\end{tabular}
%\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
%\label{notsharedbottom10}
%\end{center}
%\end{table}
%
%Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive. When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home. When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations. When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation. 
%
%On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning. When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns. When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible. When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience. However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.

\subsubsection{Device}
Participants had unique VURs for scenarios only differing in device. Our participants had a 58.79\% VUR when asked about wearables and 46.64\% VUR when asked about smartphones.The VURs for both devices for all 5 questions are in table ~\ref{deviceVUR}. However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}). Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2. The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions. Too few instances of participants answering both versions of questions occured (34 in total for all 5 questions) to perform a sound within-subjects analysis.

\begin{table}[t]
\begin{center}
\begin{tabular}{| c | r | r |}
\hline
 Question &  Wearable VUR & Smartphone VUR \\
 \hline
 All & 58.79\% & 46.64\%\\
Q1 & 14.81\%  &  6.13\%\\
Q2 & 44.11\%  &  19.85\%\\
Q3 & 87.09\%  &  58.44\%\\
Q4 & 52.77\%  & 55.74\%\\
Q5 & 86.49\%  &  91.82\%\\ 
\hline
\end{tabular}
\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
\label{deviceVUR}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{|c|r|r|r|r|}
%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
%All	2.814	0.1395	No		3589		0.001\\
%Q1	2.500	0.1139	No		714		0.004\\
%Q2	17.333	<0.0001	Yes		708		0.024\\
%Q3	0.020	0.8886	No		699		0.000\\
%Q4	1.426	0.2324	No		731		0.002\\
%Q5	1.611		0.2043	No		710		0.002\\
\hline
Question & $\chi^2$ & p-value & n & $\phi$ \\
\hline
All & 2.202 & <0.1378 & 3,588 & 0.001\\
Q1 & 2.500 & <0.1139 & 714 & 0.004\\
Q2 & 17.333 & <0.0001 & 708 &  0.024\\
Q3 & 0.020 & <0.8886 & 699 &  0.000\\
Q4 & 1.413 & <0.2345 & 730& 0.002\\
Q5 & 1.604 & <0.2054 & 709 & 0.002\\
\hline
\end{tabular}
\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
\label{betweendevice}
\end{center}
\end{table}

%\begin{table}%[h]
%\begin{center}
%\begin{tabular}{| c | c | c | c |}
%Question & $\chi^2$ &	2-tail P & Effect Size \\
%All & 0.444  & 0.505 & 0.006\\
%Q1 & 0 & 1 & 0 \\
%Q2 & 0 & 1 & 0\\
%Q3 & 0 & 1 & 0\\
%Q4 & 0 & 1 & 0\\
%Q5 & 0 & 1 & 0\\
%\end{tabular}
%\caption{Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.}
%\label{withindevice}
%\end{center}
%\end{table}

%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test. Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone). The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid. For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test.

\subsubsection{Demographic Factors}

Participants' responses were correlated with demographic factors. We observed that the biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}: a Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$). Similarly, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$). We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.

While we initially observed an effect on VURs based on whether or not participants claimed to already own wearable devices (57.0\% vs. 60.8\%, respectively; Mann-Whitney $U=202,896$, $p<0.032$), this difference did not remain significant upon correcting for multiple testing (Bonferroni corrected $\alpha=0.01$), nor did the effect of gender. Finally, we observed no correlation between education level and VUR.

\subsubsection{Regression Models} 
\label{sec:regression}
In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, device, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes). We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).

>>>>

\documentclass{acm_proc_article-sp}
\usepackage{color}
\usepackage[hyphens]{url}

\def\etal{{\it et al.~}}
\newenvironment{packed_enum}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}}
\newenvironment{packed_item}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

@@

\input{title.tex}
\input{abstract.tex}
\input{intro.tex}
\input{methodology.tex}
\input{results.tex}
\input{discussion.tex} 
\input{related_work.tex} 
\input{conclusion.tex} 
\bibliographystyle{abbrv}
\bibliography{bibliography.bib} 
\input{appendixes.tex}

\end{document}
